---
title: "HW2 Solution"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



First, build a model using salary as the response and Ht and Exp as variables and denote it as Model_1.  Build a second model using log(salary) as the response and Ht and Exp as variables, we denote it as Model_2.
```{r}
nba = read.csv("nba2017.csv", header = TRUE)
```

```{r}
str(nba)
```

First, build a model using salary as the response and Ht and Exp as variables and denote it as Model_1.  Build a second model using log(salary) as the response and Ht and Exp as variables, we denote it as Model_2.

```{r}
Model_1 <- lm(data=nba, Salary ~ Ht + Exp)
summary(Model_1)
```

```{r}
Model_2 <- lm(data=nba, log(Salary) ~ Ht + Exp)
summary(Model_2)
```

```{r}
eitc = read.csv("eitc.csv", header = TRUE)
str(eitc)
```


```{r}
eitc$postbill= as.numeric(eitc$year >1993)
eitc$kids = as.numeric(eitc$children >=1)
```


```{r}
colnames(eitc)
```


```{r}
str(eitc)
```

```{r}

before_no_kid <- subset(eitc, eitc$postbill==0 & eitc$kids == 0)
before_has_kid <- subset(eitc, eitc$postbill==0 & eitc$kids == 1)
after_no_kid <- subset(eitc, eitc$postbill==1 & eitc$kids == 0)
after_has_kid <- subset(eitc, eitc$postbill==1 & eitc$kids == 1)

```

```{r}
A = mean(before_no_kid$work)
C = mean(before_has_kid$work)
B = mean(after_no_kid$work)
D = mean(after_has_kid$work)

(D-B)-(C-A)
```

```{r}

```

