---
title: "Final"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd('/Users/alex/Library/Mobile Documents/com~apple~CloudDocs/MS Analytics/GT OMSA/SP20 MGMT 6203/Final/')
```

```{r}
# packages

library(dplyr)
library(caret)
library(xts)
library(PerformanceAnalytics)

```


```{r}
df <- read.csv('direct_marketing.csv', header=TRUE)

str(df)
head(df, 10)

```

We are interested in the effects of categorical variable ‘Gender’ and numerical variable ‘Salary’ on 'AmountSpent’. After running the linear regression of ‘AmountSpent’ on ‘Gender’ and ‘Salary’,

```{r}
lm_1 <- lm(AmountSpent~Gender+Salary, data=df)
summary(lm_1)
```

Convert the Married column into a dummy variable with ‘Married’ being 1 and ‘Single’ being 0.  Now create another model for AmountSpent regressed against Gender, Salary and Married. Based off your model, how much more (or less) would a married person spend than a single person? (Assume arbitrary units)

```{r}
df <- df %>% 
  mutate(Married_v = as.factor(if_else(Married=='Married',1,0)))

lm_2 <- lm(AmountSpent~Gender+Salary+Married_v, data=df)
summary(lm_2)

```

```{r}
library(MASS)
```

```{r}
str(Boston)
```

```{r}
df_2 <- Boston %>% 
  mutate(medv = as.factor(if_else(medv>30,1,0)))

glm_3 <- glm(medv~., data = df_2, family = 'binomial')
summary(glm_3)
```
3. 
A. If rm increases by 1 unit, the natural log of the odds of the house median value being greater than $30,000 increases by 2.3549.

4.What is the Sensitivity of the model?

```{r}
df_2$predict_result <- predict(glm_3, df_2, type='response')
df_2$predict_medv <- as.factor(if_else(df_2$predict_result>0.5,1,0))


confusionMatrix(df_2$predict_medv, df_2$medv, dnn=c("Prediction", "Reference"), positive='1')


```

5.What is the AUC (Area Under the Curve) for this model?

```{r}
library(ROCR)

#ROC Curve
pred <- prediction(df_2$predict_result,df_2$medv) 
class(pred)
# calculate Area Under the Curve for this Logit Model
auc.perf <-  performance(pred, measure = "auc")
auc.perf@y.values
```


6.What is the Sharpe Ratio across the period 10/22/2019 to 11/22/2019 for Amazon.com? (Please use arithmetic return and omit 10/22 when you calculate Sharpe Ratio, i.e.: only 23 data points are used to calculate Sharpe Ratio)
```{r}
df_6 <- read.csv('AMZN.csv';)


```

